Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2019-04-09 thesis/chapters/ch_introduction.tex
new references
fixed italics

%Developing a complete model for galactic chemical evolution is a daunting task.
To give an impression of the difficulties involved, we outline a recipe for constructing a complete model of galactic chemical evolution. One must first prescribe a galaxy's connection to its large scale structure to understand the inflow of pristine, metal-free gas into the disk of the galaxy, and the accretion (via mergers) of stars formed previously in galaxies hosted by different dark matter halos. One can then worry about knowing where, when, how, and with what masses stars form in the first place from this gas. This requires understanding the hydrodynamic
%and magnetohydrodynamic
properties of the multi-scale, multi-phase turbulent interstellar medium (ISM) and the radiative processes and chemistry that operate within the ISM. This in turn requires one to toss in a detailed understanding of the stellar feedback physics -- stellar radiation, stellar winds, and supernovae -- that helps to regulate star formation by destroying cold, star forming gas, driving the multi-phase structure of the ISM, and by driving outflows of gas into the circumgalactic medium (CGM) around galaxies. Simultaneously, one makes the simple step of nailing down a complete model of stellar structure, stellar evolution, the reaction rates and cross sections of every nuclear reaction, and the lifetimes of individual isotopes. Once all of this is understood, one can then color in the gas in the galaxy over time with the individual metal yields of stellar populations released over their lifetime. With a complete understanding of stellar feedback and the ISM, one can then be sure that they completely capture the mixing of these metals in the ISM over time, and will produce a stellar population with accurate metal abundance ratios. In addition, one would then produce realistic galactic winds, removing the correct amount of metals from the galaxy and enriching the CGM and the intergalactic medium (IGM). Finally, one can layer this model ad nauseum on top of a $\Lambda CDM$ model for the cosmological evolution of many galaxies, reproducing all observed properties of galactic chemical evolution as a function of both mass and redshift..... Wait... I forgot about magnetic fields, active galactic nuclei, and cosmic rays...

@@

Stellar feedback drives outflows, galactic winds, from galaxies across all scales
%(references).
Dwarf galaxies in particular, with their relatively shallow potential wells, are expected to drive effective galactic winds \citep{MacLowFerrara1999} with mass loading factors ($\eta$ = $\dot{\rm{M}}_{\rm out} / {\rm SFR}$) above 100 \citep{Muratov2015,Christensen2018}. Not only does this correspond to a significant amount of mass outflow from these galaxies, but these winds should also carry out a substantial amount of metals from these galaxies. \cite{Kirby2011-metals} used measurements of the stellar abundances in Local Group dSph's and their resolved star formation histories to determine that their stars contain less than 5\% of the metals synthesized in each galaxy. However, since these galaxies have lost their gas through environmental processes as satellites of the Milky Way (primarily ram pressure and tidal stripping), it was unclear if this loss could be attributed entirely to feedback. However, using gas and stellar abundances \cite{McQuinn2015} showed that Leo P -- a gas-rich Local Group dwarf galaxy -- has also ejected $\sim$95\% of its metals (see Section~\ref{intro:sec:Leo P}). This is significant evidence for metal-enriched, feedback-driven galactic winds operating in these low mass dwarf galaxies.

>>>>

%Developing a complete model for galactic chemical evolution is a daunting task.
To give an impression of the difficulties involved, we outline a recipe for constructing a complete model of galactic chemical evolution. One must first prescribe a galaxy's connection to its large scale structure to understand the inflow of pristine, metal-free gas into the disk of the galaxy, and the accretion (via mergers) of stars formed previously in galaxies hosted by different dark matter halos. One can then worry about knowing where, when, how, and with what masses stars form in the first place from this gas. This requires understanding the hydrodynamic
%and magnetohydrodynamic
properties of the multi-scale, multi-phase turbulent interstellar medium (ISM) and the radiative processes and chemistry that operate within the ISM. This in turn requires one to toss in a detailed understanding of the stellar feedback physics -- stellar radiation, stellar winds, and supernovae -- that helps to regulate star formation by destroying cold, star forming gas, driving the multi-phase structure of the ISM, and by driving outflows of gas into the circumgalactic medium (CGM) around galaxies. Simultaneously, one makes the simple step of nailing down a complete model of stellar structure, stellar evolution, the reaction rates and cross sections of every nuclear reaction, and the lifetimes of individual isotopes. Once all of this is understood, one can then color in the gas in the galaxy over time with the individual metal yields of stellar populations released over their lifetime. With a complete understanding of stellar feedback and the ISM, one can then be sure that they completely capture the mixing of these metals in the ISM over time, and will produce a stellar population with accurate metal abundance ratios. In addition, one would then produce realistic galactic winds, removing the correct amount of metals from the galaxy and enriching the CGM and the intergalactic medium (IGM). Finally, one can layer this model ad nauseum on top of a $\Lambda$CDM model for the cosmological evolution of many galaxies, reproducing all observed properties of galactic chemical evolution as a function of both mass and redshift..... Wait... I forgot about magnetic fields, active galactic nuclei, and cosmic rays...

@@

Stellar feedback drives outflows, galactic winds, from galaxies across all scales
%(references).
Dwarf galaxies in particular, with their relatively shallow potential wells, are expected to drive effective galactic winds \citep{MacLowFerrara1999} with mass loading factors ($\eta$ = $\dot{\rm{M}}_{\rm out} / {\rm SFR}$) above 100 \citep{Muratov2015,Christensen2018}. Not only does this correspond to a significant amount of mass outflow from these galaxies, but these winds should also carry out a substantial amount of metals from these galaxies. In fact, the differences with which different models for feedback-driven winds drive metals in outflows in low mass galaxies can be an important constrain on the underlying physics \citep[e.g.]{Wheeler2018,Agertz2019}. \cite{Kirby2011-metals} used measurements of the stellar abundances in Local Group dSph's and their resolved star formation histories to determine that their stars contain less than 5\% of the metals synthesized in each galaxy. However, since these galaxies have lost their gas through environmental processes as satellites of the Milky Way (primarily ram pressure and tidal stripping), it was unclear if this loss could be attributed entirely to feedback. However, using gas and stellar abundances \cite{McQuinn2015} showed that Leo P -- a gas-rich Local Group dwarf galaxy -- has also ejected $\sim$95\% of its metals (see Section~\ref{intro:sec:Leo P}). This is significant evidence for metal-enriched, feedback-driven galactic winds operating in these low mass dwarf galaxies.
